---
title: |
  |
  | 
  | \vspace{1cm}Be Safe, Be Smart, Be Kind
  | An Investigation in the Stigma of COVID-19*^[*Corresponding address: hensgensophie Acknowledgments: I am grateful to all those generous people that invest their time into open-source software.]\vspace{0.5cm}
  |
author: |
  | Sophie Katharina Hensgen
  | University of Mannheim - Faculty of Social Science
  | Matricle Number: 1560750
  | shensgen@mail.uni-mannheim.de
  | Böckstraße 15, 68159 Mannheim
  | Telephone number: 0152 32735703
date: |
  |       
  | `r gsub("^0", "", format(Sys.time(), "%B %d, %Y"))`
  |
  | [Github repository](https://github.com/SophieHensgen/stigmatization-Covid-19.git)
abstract: "Here will be the abstract of my paper"
keywords: "stigmatization stigma COVID-1ß Coronavirus responsibility"
header-includes:
    - \usepackage{setspace}\doublespacing
    - \usepackage{booktabs}
    - \usepackage{capt-of}
    - \usepackage{floatrow}
    - \floatsetup[figure]{capposition=top}
    - \floatsetup[table]{capposition=top}
#geometry: margin = 3cm
#fontfamily: timesnewroman
fontsize: 12pt 
output:
  pdf_document:
    toc: yes
    df_print: kable
    number_sections: true
always_allow_html: true
bibliography: Bib.bib
---

```{packages, include=FALSE}

```

# Introduction

"Be safe, be smart, be kind" - with these words, Dr. Tedros Adhanom Ghebreyesus, the Director-General of WHO, launched WHO's "Be Ready" campaign in the   beginning of March 2020 [@who_be_2020]. A few days before the first lockdown in Germany, Ghebreyesus warned about the risk that would come with the spread of COVID-19. His message in the wake of the campaign is straightforward. However, to follow his advice seems to be harder than one might think.
This pandemic is hard on everyone.  We are watching more and more people die every day, restaurants and shops have to close for good  and everybody else is restricted in their day to day life. 

```{r}

```

## 


```{r}

```
\newpage

# References

<div id="refs"></div>

\clearpage

\textbf{Statutory Declaration}

Students shall include a bibliography in all their term papers and project-related papers and submit a signed declaration with the following wording:

„I hereby declare that the paper presented is my own work and that I have not called upon the help of a third party. In addition, I affirm that neither I nor anybody else has submitted this paper or parts of it to obtain credits elsewhere before. I have clearly marked and acknowledged all quotations or references that have been taken from the works of other. All secondary literature and other sources are marked and listed in the bibliography. The same applies to all charts, diagrams and illustrations as well as to all Internet sources. Moreover, I consent to my paper being electronically stores and sent anonymously in order to be checked for plagiarism. I am aware that the paper cannot be evaluated and may be graded “failed” (“nicht ausreichend”) if the declaration is not made.”

For term papers and project-related papers in English, the English declaration shall be included as well.

Place, Date: Mannheim, 27.07.2020


Signature:
(Sophie Hensgen)

